### 2017-09-19 old/documents/BrazilSlides/Archive Versions/slides_for_rob.tex
reformat github repo

\documentclass[
    hyperref={bookmarks=false},% ,, linkcolor=blue, urlcolor=blue,, colorlinks=true, citecolor=MidnightBlue
    xcolor={dvipsnames},
]{beamer}

@@

% \usepackage{pgfpages} % For viewing slides on the right
\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
\AtBeginNote{\scriptsize} % Make notes small
% \setbeameroption{show notes} % Shows notes
% \setbeameroption{show only notes} % Shows only notes
% \setbeameroption{show notes on second screen}
\usefonttheme[onlymath]{serif} % For serif font in math mode
\usepackage[backend=biber, style=authoryear, doi=false,isbn=false,url=false, citestyle=authoryear-comp]{biblatex} %

\setbeamertemplate{navigation symbols}{
\insertslidenavigationsymbol%
\insertframenavigationsymbol%
\insertsubsectionnavigationsymbol%
\insertsectionnavigationsymbol%
\insertdocnavigationsymbol%
\insertbackfindforwardnavigationsymbol%
\hspace{1em}%
\usebeamerfont{footline} \insertframenumber/\inserttotalframenumber%
}

\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

\usepackage{silence}
\WarningFilter{biblatex}{Patching footnotes failed}
\renewcommand\mkbibacro[1]{{\footnotesize\MakeUppercase{#1}}} % http://tex.stackexchange.com/questions/203111/small-caps-font-warning-in-beamer-using-biblatex

\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}
\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots
\setbeamertemplate{bibliography item}{\insertbiblabel}
\addbibresource{../references.bib}
\AtBeginBibliography{\small}

\newcommand{\probplotvalue}[1]{%
    \definecolor{probvalcolor}{RGB}{#1}%
    \definecolor{outlinecolor}{RGB}{127, 127, 127}%
    \begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]%
        \pgfmathsetmacro{\size}{0.2};%
        \draw[outlinecolor, fill=probvalcolor] (-\size,-\size) -- (-\size, +\size) -- (+\size, +\size) -- (+\size, -\size) -- cycle;%
    \end{tikzpicture}%
}%

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.C.~Fraser\inst{1,2}}
\institute
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada \\
    \inst{2}%
    University of Waterloo\\
    Ontario, Canada \\
}
\date[QN 2016]{Quantum Networks Workshop, IIP, Nov. 2016}

@@

\begin{frame}
    \titlepage
    \note[item]{Thank International Institute for Physics (IIP) for support}
    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
\end{frame}

\begin{frame}
    \frametitle{The Triangle Scenario (TS)}
    \begin{center}
        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
    \end{center}
    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
    \note[item]{Triangle Scenario has be studied extensively before}
    \note[item]{In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}}
    \note[item]{In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}
    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)}
    \note[item]{Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective}
\end{frame}

\begin{frame}
    \frametitle{This Talk}
    \begin{enumerate}
        \item Inflation technique provides polynomial inequalities
        \item Inequalities witnessing non-local quantum correlations in the Triangle Scenario
        \item Discuss search for new non-local quantum correlations
    \end{enumerate}
    \note[item]{This talk is going to have three components}
    \note[item]{Demonstrating how something called the inflation technique allows one derive polynomial compatibility constraints for and causal structure}
    \note[item]{Using the inflation technique to find inequalities that demonstrate non-local quantum distributions on the Triangle scenario}
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility}
    \vfill
    \begin{center}
        Triangle Scenario
    \end{center}
    \[ \prob[ABC] = \int_{XYZ}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    \vfill
    \begin{center}
        \noindent\rule{8cm}{0.4pt}
    \end{center}
    \vfill
    \begin{center}
        General Setting
    \end{center}
    \begin{align*}
    \mscenario &= \bc{V_1, \ldots, V_n} \\
    \prob^{\mscenario} &= \bc{\prob[V_1], \ldots, \prob[V_n]}
    \end{align*}
    \[ \forall V \in \mscenario: \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
    \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
    \vfill
\end{frame}

\section{Part 1: Inflation Technique}
\begin{frame}
    \frametitle{Demonstrating Inflation Technique}
    \vfill
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_1}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_1}}
    \end{columns}
    \end{center}
    \only<1>{\[\forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n}\]}%
    \only<2>{\[\AnSub[\graph]{A} \sim \AnSub[\graph']{A_1}\]}%
    \only<3>{\[\AnSub[\graph]{C} \sim \AnSub[\graph']{C_2}\]}%
\end{frame}

\begin{frame}
    \frametitle{Some Inflations of the Triangle Scenario}
    \begin{center}
    \begin{tabular}{cc}
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/triangle_scenario}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral}}
        \\
        %\hline
        The Triangle Scenario
        &
        Spiral Inflation \\
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
        \\
        %\hline
        Cut Inflation
        &
        Large Inflation \\
        %\hline
    \end{tabular}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{What are Injectable Sets?}
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_2}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_2}}
    \end{columns}
    \end{center}
    \only<1>{\[\AnSub[\graph]{A,C} \sim \AnSub[\graph']{A_2,C_1}\]}%
    \only<2>{\[?? \not \sim \AnSub[\graph']{B_1,B_2}\]}%
    \only<3>{\[?? \not \sim \AnSub[\graph']{B_2,C_2}\]}%
\end{frame}

\begin{frame}
    \frametitle{Injectable Sets Defined}
    \vfill
    The \term{injectable sets in $\graph'$}:
    \begin{align*}
        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
    The \term{images of the injectable sets in $\graph$}:
    \begin{align*}
        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
    \vfill
    \begin{center}
        \textbf{What makes injectable sets useful?}
    \end{center}
    \vfill
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma}
    \begin{lemma}[Inflation Lemma]
    Given $\graph = \br{\nodes, \edges}$ and inflation $\graph' = \br{\nodes', \edges'}$:
    \begin{center}
        \begin{tikzpicture}
            \pgfmathsetmacro{\vs}{2.2};
            \pgfmathsetmacro{\hs}{5.2};
            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
            \draw[very thick, ->] (pn) -- (cp);
            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
            \draw[very thick, ->] (cp_) -- (pn_);
        \end{tikzpicture}
    \end{center}
    \end{lemma}
\end{frame}

\begin{frame}
    \frametitle{Perfect Correlation Is Incompatible}
    \begin{columns}
        \column{0.5\linewidth}
        \begin{center}
            \includegraphics[width=\linewidth]{../../figures/distributions/perfect_correlation_2_outcomes.pdf}
        \end{center}
        \column{0.5\linewidth}
        \begin{align*}
        \probplotvalue{0, 0, 0} &= \f12 \\
        \prob[ABC][abc] &= \f{\bs{000} + \bs{111}}{2} \\
        \prob[ABC][abc] &= \begin{cases}
            \f12 & a = b = c \\
            0 & \text{ otherwise }
        \end{cases}
        \end{align*}
    \end{columns}
    \begin{center}
        Compatibility Inequality
    \end{center}
    \[ \prob[A][0]\prob[B][1] \leq \prob[BC][10] + \prob[AC][01] \]
    \begin{center}
        Witnesses Perfect Correlation
    \end{center}
    \[ \br{\f{1}{2}}^{2} \not\leq 0 + 0 \]
\end{frame}
\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother
\begin{frame}
    \frametitle{Deriving Compatibility Inequalities}
    \begin{center}
        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
    \end{center}
    \[ \mscenario = \bc{\bc{A_1, B_1}, \bc{B_1, C_1}, \bc{A_1, C_1}} \]
    \[ \prob^{\mscenario} = \bc{\prob[A_1B_1], \prob[B_1C_1], \prob[A_1C_1]} \]
    \[ \text{Compatibility requires:} \qquad \exists \prob[\jointvar] = \prob[A_1B_1C_1] \]
    \[ \prob[A_1B_1] = {\sum}_{C_1} \prob[\jointvar] \qquad \prob[B_1C_1] = {\sum}_{A_1} \prob[\jointvar] \qquad \prob[A_1C_1] = {\sum}_{B_1} \prob[\jointvar]\]
\end{frame}

\begin{frame}[shrink=13]
    \frametitle{Deriving Compatibility Inequalities Cont'd}
    \[ \underbrace{\prob[A_1B_1] = {\sum}_{C_1} \prob[\jointvar] \qquad \prob[B_1C_1] = {\sum}_{A_1} \prob[\jointvar] \qquad \prob[A_1C_1] = {\sum}_{B_1} \prob[\jointvar]} \]
    \[ \underbrace{\forall V \in \mscenario: \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] }\]
    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}  \]
    \[ \probvec^{\mscenario} =
        \begin{pmatrix}
            \prob[A_1B_1][00] \\
            \prob[A_1B_1][01] \\
            \prob[A_1B_1][10] \\
            \prob[A_1B_1][11] \\
            \hline
            \prob[B_1C_1][00] \\
            \prob[B_1C_1][01] \\
            \prob[B_1C_1][10] \\
            \prob[B_1C_1][11] \\
            \hline
            \prob[A_1C_1][00] \\
            \prob[A_1C_1][01] \\
            \prob[A_1C_1][10] \\
            \prob[A_1C_1][11] \\
        \end{pmatrix}
        \qquad
        \probvec^{\jointvar} =
        \begin{pmatrix}
            \prob[A_1B_1C_1][000] \\
            \prob[A_1B_1C_1][001] \\
            \prob[A_1B_1C_1][010] \\
            \prob[A_1B_1C_1][011] \\
            \prob[A_1B_1C_1][100] \\
            \prob[A_1B_1C_1][101] \\
            \prob[A_1B_1C_1][110] \\
            \prob[A_1B_1C_1][111] \\
        \end{pmatrix}
    \]
\end{frame}

\begin{frame}[shrink=15]
    \frametitle{Incidence Example}
    \[ M = \kbordermatrix{
        (A_1,B_1,C_1) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
        (A_1=0, B_1=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
        (A_1=0, B_1=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
        (A_1=1, B_1=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
        (A_1=1, B_1=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
        (B_1=0, C_1=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
        (B_1=0, C_1=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
        (B_1=1, C_1=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
        (B_1=1, C_1=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
        (A_1=0, C_1=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
        (A_1=0, C_1=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
        (A_1=1, C_1=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
        (A_1=1, C_1=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
    } \]
    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}  \]
\end{frame}

\begin{frame}
    \frametitle{Marginal Linear Program}
    \begin{columns}[T]
        \column{0.4\linewidth}%
            \term{Marginal LP}:%
            \begin{alignat*}{2}
                & \text{minimize:} \quad&& \emptyset \tcdot x\\
                & \text{subject to:} && \probvec^{\jointvar} \succeq 0 \\
                & && M \tcdot \probvec^{\jointvar} = \probvec^{\mscenario} \\
            \end{alignat*}%
        \column{0.4\linewidth}%
            \term{Dual Marginal LP}:%
            \begin{alignat*}{2}
                & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
                & \text{subject to:} && y \tcdot M \succeq 0 \\
            \end{alignat*}%
    \end{columns}
    \begin{itemize}
        \item If $\probvec^{\jointvar}$ exists, then:
        \[ y \tcdot M \tcdot \probvec^{\jointvar} = y \tcdot \probvec^{\mscenario} \geq 0  \]
        \item If not, then $y$ is an \term{infeasibility certificate} which generates \term{infeasibility inequality}:
        \[ y \tcdot \probvec^{\mscenario} \geq 0 \]
        \item Most linear programing toolkits return certificates (\href[pdfnewwindow]{http://docs.mosek.com/8.0/pythonapi/optimizer-task-gety.html}{\textit{Mosek}}, \href[pdfnewwindow]{https://www.gurobi.com/documentation/6.5/refman/farkasdual.html}{\textit{Gurobi}}, \href[pdfnewwindow]{http://www-01.ibm.com/support/docview.wss?uid=swg21400058}{\textit{CPLEX}}, \href[pdfnewwindow]{http://cvxr.com/cvx/doc/basics.html\#dual-variables}{\textit{cvxr}}/\href[pdfnewwindow]{http://cvxopt.org/userguide/coneprog.html\#linear-cone-programs}{\textit{cvxopt}}.)
    \end{itemize}
    \note[item]{It is possible to derive non-contextuality inequalities from $M$ and a known incompatible distribution $\probvec^{\mscenario}$}
    \note[item]{Note the null objective; the minimization objective is trivially always zero}
    \note[item]{The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.}
    \note[item]{If \textit{feasible}, then there exists a vector $x$ that is a valid joint distribution vector $\probvec^{\jointvar}$.}
    \note[item]{Feasibility implies that $\probvec^{\jointvar} = x$.}
    \note[item]{Infeasibility implies contextuality}
\end{frame}

\begin{frame}
    \frametitle{Deflating Inequalities}
    \begin{columns}
        \column{0.5\linewidth}
            \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut_anim_1}}
        \column{0.5\linewidth}
            \vfill
            \begin{center}
            \[ \Inj[\graph]{\graph'} = \begin{Bmatrix}
                \bc{A_1,C_1}\\ \bc{B_1,C_1}\\ \bc{A_1}\\ \bc{B_1}\\ \bc{C_1}
            \end{Bmatrix} \]
            \[ \bc{A_1, B_1} \not \in \Inj[\graph]{\graph'} \]
            \end{center}
            \vfill
    \end{columns}
    \[ \prob[A_1B_1][01] \leq \prob[B_1C_1][10] + \prob[A_1C_1][01] \]
    \only<1>{\begin{center}\textbf{Can not deflate inequality!}\end{center}}
    \only<2>{\begin{center}\textbf{However!}\end{center}}
    \only<2>{\[ \AnSub[\graph']{A_1} \cap \AnSub[\graph']{B_1} = \emptyset \iff A_1 \ancestralindep B_1 \]}
    \onslide<3->{\[ \prob[A_1][0]\prob[B_1][1] \leq \prob[B_1C_1][10] + \prob[A_1C_1][01] \]}
    \onslide<4->{\[ \prob[A][0]\prob[B][1] \leq \prob[BC][10] + \prob[AC][01] \]}
\end{frame}

\begin{frame}
    \frametitle{Inflation Gives Polynomial Inequalities}
    \begin{itemize}
        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
        \item \textbf{Linear inequality} for $\graph'$
    \end{itemize}
    \begin{center}
        \begin{tikzpicture}[scale=0.8]
            \pgfmathsetmacro{\hs}{1.8};
            \pgfmathsetmacro{\vs}{1};
            \pgfmathsetmacro{\cross}{0.3};
            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
            \draw (0, 0) node[](b){??};
            \draw[thick, ] (a) -- (ab);
            \draw[thick, ] (c) -- (cd);
            \draw[thick, ] (a) -- (ac);
            \draw[thick, ->] (ac) -- (c);
            \draw[thick, ->] (ab) -- (b);
            \draw[thick, ->] (cd) -- (d);
            \draw[very thick, red]
            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
            ;
        \end{tikzpicture}
    \end{center}
    \begin{itemize}
        \item \textbf{Polynomial inequality} for $\graph$!
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pre-injectable Sets}
    A \term{pre-injectable set} $N'$ is:
    \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
    \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
    Only need to consider \term{maximal pre-injectable sets} denoted $\PreInj[\graph]{\graph'}$
\end{frame}

\section{Part 2: Quantum Non-locality From Inflation}

\begin{frame}
    \frametitle{Quantum Correlation}
    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Triangle Scenario As Bell Scenario}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational_fritz_bell}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_brazil.pdf}
    \end{center}
    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution Bit-Measurements}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_bits_brazil.pdf}
    \end{center}
    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \quad \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2}
    \end{gather*}
    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
        M_{B} = \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution Violating CHSH}
    % \begin{gather*}
    % \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
    % \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
    % \end{gather*}
    \begin{itemize}
        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
        \item Correlation between right bits
    \end{itemize}
    \[ \ba{A_rB_r} = \prob[A_rB_r][00] + \prob[A_rB_r][11] - \prob[A_rB_r][01] - \prob[A_rB_r][10] \]
    \[ \ba{A_rB_r | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{A_rB_r | C = 3} = - \f{1}{\sqrt{2}} \]
    \begin{itemize}
        \item Gives CHSH violation
    \end{itemize}
    \begin{align*}
    &\ba{A_rB_r|C=0} + \ba{A_rB_r|C=1} + \ba{A_rB_r|C=2} - \ba{A_rB_r|C=3} \\
    &\quad = 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} \\
    &\quad = 2\sqrt{2} \not \leq 2
    \end{align*}
\end{frame}

\begin{frame}
    \frametitle{Notes on Fritz Distribution}
    \begin{itemize}
        \item Incompatibility proof contingent on perfect correlation between $C$ and pseudo-settings
        \item Proof not robust to noise
    \end{itemize}
    \begin{problem}[2.17 in \cite{Fritz_2012}]
        Find an example of non-classical quantum correlations in TS together with a proof of its non-classicality which does not hinge on Bell’s Theorem.
    \end{problem}
    \begin{itemize}
        \item ``...would be helpful to have inequalities...''
        % \item Possible to find inequalities violated by $\prob[F]$ using the Large inflation of the TS
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Large Inflation}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Large Inflation Pre-injectable Sets}
    \begin{equation*}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
\end{frame}

% \begin{frame}
%     \frametitle{Deriving Inequalities}
%     \begin{itemize}
%         \item Inflation facilitates turning linear, inflated inequalities into polynomial deflated ones
%         \item \textbf{Question:} How to derive compatibility inequalities for $\graph'$?
%         \item \textbf{Answer:} Use your favorite technique for deriving compatibility inequalities:
%         \begin{itemize}
%             \item Entropic inequalities
%             \item Finite outcome inequalities
%         \end{itemize}
%         \item Here we solve the marginal problem for $\mscenario = \PreInj[\graph]{\graph'}$
%         \item First some notation and formalism
%     \end{itemize}
% \end{frame}

\begin{frame}
    \frametitle{Large Inflation Incidence}
    \begin{itemize}
        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
        \item Inequalities violated by Fritz distribution are inherently $4$-outcome
        \item Incidence matrix $M$ is \textbf{very large} $\sim 2.25 \textsf{Gb}$
        \begin{itemize}
            \item $\# \text{Columns} = 4^{12} = 16,777,216$
            \item $\# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896$
            \item $\# \text{Non-zero Entries} = 201,326,592$
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Certificate for Fritz Distribution}
    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
    \vfill
    \textbf{Note:} $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
\end{frame}

\begin{frame}[shrink=64]
    \frametitle{Certificate for Fritz Distribution (Full)}
    \begin{center}
        \input{../../figures/inequalities/nosymwitness_ineq_print}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Symmetric Inequalities}
    \begin{itemize}
        \item Certificate inequalities are curated/constructed to witness violation of particular distribution
        \item Above inequality not the best candidate to search for non-locality different than Fritz distribution
        \item Perhaps one could obtain inequality that does not assign special preference to $C$
        \item Desirable to find compatibility inequality $I$ such that
        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Party Symmetric Inequality}
    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print_pretty}
    \vfill
    \textbf{Note:} $\bs{\prob[][113]\prob[][330]}_3$ shorthand sum over permutations:
    \[ \prob[][113]\prob[][330] + \prob[][131]\prob[][303] + \prob[][311]\prob[][033] \]
\end{frame}

\begin{frame}[shrink=60]
    \frametitle{Party Symmetric Inequality (Full)}
    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
\end{frame}

\section{Part 3: Maximal Violations \& Noise}

\begin{frame}
    \frametitle{Numerical Optimization}
    Minimize objective function $f\br{\la} \in \R$:
    \begin{enumerate}
        \item Real-valued parameters $\la = \br{\la_0, \ldots, \la_n}$
        \item Quantum states/measurements $\rho_{AB}, \rho_{BC}, \rho_{CA}, M_{A}, M_{B}, M_{C}$
    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
        \item Distribution $\prob[ABC]$
        \item Plug into inequality $I$ in homogeneous form $I\br{\prob[ABC]} \geq 0$
        \item Output is objective value $I\br{\prob[ABC]}$
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Numerical Optimization Methods}
    \begin{itemize}
        \item Numerical minimization of $f\br{\la}$
        \[ f(\la_{(k+1)}) = \la_{(k)} - \ga_{(k)} \del f(\la_{(k)})  \]
        \item Non-convex, non-linear, smooth/continuous
        \item Gradient Descent, BFGS Method, Nelder-Mead simplex method
        \item Stochastic methods: simulated annealing, basin-hopping
    \end{itemize}
\end{frame}

>>>>

\documentclass[]{beamer}

@@

@@
